{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-13 thesis/intro.tex
how to read the thesis

\begin{itemize}
	\item {\bf Background:} Chapter~\ref{chap:background} will present the requisite background material on concurrent programming, stateless model checking, and the various types of programs targeted by Landslide.
	\item {\bf Landslide:} Chapter~\ref{chap:landslide} explains the design and implementation of Landslide
		%the core of my stateless model checking framework,
		and all the special features it's been equipped with over the years.
	\item {\bf Quicksand:} Chapter~\ref{chap:quicksand} presents the Iterative Deepening framework which more intelligently chooses which state spaces to test, corresponding to contribution 1 above.
	\item {\bf Education:} Chapter~\ref{chap:education} discusses my evaluation of Landslide
		in CMU's 15-410 class environment using the Pebbles kernel,
		and in the University of Chicago's and Berkeley's OS class environments using the Pintos kernel,
		corresponding to contribution 2 above.
	%\item {\bf Pebbles:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in CMU's 15-410 class environment using the Pebbles kernel, corresponding to contribution 2 above.
	%\item {\bf Pintos:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in the University of Chicago's and Berkeley's OS class environments using the Pintos kernel, corresponding to contribution 2 above.
	\item {\bf Transactional Memory:} Chapter~\ref{chap:tm} presents my extension of Landslide's concurrency model to handle transactional concurrency and the evaluation thereof, corresponding to contribution 3 above.
	\item {\bf Related Work:} Chapter~\ref{chap:relatedwork} honors my neighbours and ancestors in research spirit.
	\item {\bf Conclusion:} Chapter~\ref{chap:conclusion} provides some thoughts on the future of the field.
\end{itemize}

>>>>

\begin{itemize}
	\item {\bf Background:} Chapter~\ref{chap:background} will present the requisite background material on concurrent programming, stateless model checking, and the various types of programs targeted by Landslide.
	\item {\bf Landslide:} Chapter~\ref{chap:landslide} explains the design and implementation of Landslide
		%the core of my stateless model checking framework,
		and all the special features it's been equipped with over the years.
		It is the foundation upon which all three contributions above build.
	\item {\bf Quicksand:} Chapter~\ref{chap:quicksand} presents the Iterative Deepening framework which more intelligently chooses which state spaces to test, corresponding to contribution 1 above.
	\item {\bf Education:} Chapter~\ref{chap:education} discusses my evaluation of Landslide
		in CMU's 15-410 class environment using the Pebbles kernel,
		and in the University of Chicago's and Berkeley's OS class environments using the Pintos kernel,
		corresponding to contribution 2 above.
	%\item {\bf Pebbles:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in CMU's 15-410 class environment using the Pebbles kernel, corresponding to contribution 2 above.
	%\item {\bf Pintos:} Chapter~\ref{chap:410} discusses my evaluation of Landslide in the University of Chicago's and Berkeley's OS class environments using the Pintos kernel, corresponding to contribution 2 above.
	\item {\bf Transactional Memory:} Chapter~\ref{chap:tm} presents my extension of Landslide's concurrency model to handle transactional concurrency and the evaluation thereof, corresponding to contribution 3 above.
	\item {\bf Related Work:} Chapter~\ref{chap:relatedwork} honors my neighbours and ancestors in research spirit.
	\item {\bf Future Work:} Chapter~\ref{chap:warpzone} % TODO
	\item {\bf Conclusion:} Chapter~\ref{chap:conclusion} provides some thoughts on the future of the field.
\end{itemize}

\subsubsection{How to read this thesis}

I have made an effort to make this document accessible to readers of all programming experience levels,
although some of the research being theoretical and several layers of abstractions deep,
I cannot promise all easy reading.
The Background chapter~(\ref{chap:background}) provides what I hope are friendly concrete examples
to help an reader feel comfortable with each level of intuition that upcoming algorithms will build upon.
These should suffice for the experiments and overall contributions,
if not necessarily the details of each algorithm or soundness proof.
The Education chapter~(\ref{chap:education}) in particular
may be approached with no knowledge of concurrency or model checking,
taking it merely as a study of a magic new debugging tool in the classroom setting.
The more ambitious reader may proceed to the Landslide chapter's further examples~(\sect{\ref{sec:landslide-algs}}),
which should equip them to understand every detail herein.
Readers who did not come to read this end-to-end should at least consult the glossary~(\sect{\ref{sec:glossary}})
to help clarify any terminology confusion.

Color will be used in figures and graphs to add visual contrast and make the data easier to navigate at a glance,
but only in redundant ways also signaled by symbols.
I have made some effort to choose palettes friendly to color-blindness,
but should the reader find contrasts too low anyway,
whether being color-blind or reading a physical copy printed in greyscale,
they may be assured all important distinctions still render in monochrome;
for example, ovals and rectangles to depict different threads,
or $\dagger$ to distinguish state space estimates from completed verifications.

Pronoun use will vary between specific singular and ambiguously-singular-or-plural to convey additional nuance.
The singular ``I'' will present my own research contributions,
while the royal ``we'' should be taken to include the reader,
such as when surveying background material or related work,
to which the author's and reader's relationships are more similar.
The abstract ``the programmer'' (or ``the user'') will be referred to as ``she''
to highlight her role as the intended audience for concurrency testing tools
rather than the underlying research,
although real students who participated in the user studies will be given the more inclusive ``they''.
Gender-neutral pronouns are to be used on the author themself.

% TODO:
% Finally, this thesis also contains a small puzzle-hunt to reward dedicated readers who make it all the way through.
